Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-31 ms.tex
more on dipole fits

We have performed one regression per HFI band to simultaneously 
fit for the zero level offset, the slope relative to 857 GHz, and the residual 
dipole amplitude. For each 100-545 GHz HFI band, we restrict tor regions of low
column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
$-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$) and fit the following model:

% At 353 GHz, 545 GHz, 857 GHz, we have 
% adopted the zero-point offsets of \cite{planckdust} Table 1, which were 
% derived by correlating \PLANCK~857 GHz versus H\,\textsc{i} at low column 
% density, and
%then by correlating the other \PLANCK~channels against the corrected 857 GHz 
%map. We have not altered the \verb|i100| zero-point in any way. We have also 
%removed the Solar dipole residual according to \cite{planckdust}, by 
%subtracting a dipole pattern oriented toward 
%$(l, b) = (263.99^{\circ}, 48.26^{\circ})$ and scaled according to their 
%Table \ref{table:offs}.

%The offset and residual dipole parameters for \PLANCK~217 GHz were not 
%available from \cite{planckdust} Table 1. In order to set the zero-point of 
%Galactic emission in the 217 GHz map, we simultaneously fit the constant 
%offset and residual dipole amplitude. Restricting to regions of low column 
%density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for $-72$$<$$v_{LSR}$$<$$+25$ 
%km\,s$^{-1}$), we modeled the 217 GHz map as:

\begin{equation} \label{equ:dip}
\mathcal{I}_{\nu_i, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_{p} + c
\end{equation}

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: a, b, and c. $a$ represents
the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz assuming 
they are linearly related. $b$ represents the scaling of the Solar dipole that 
makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. 
$c$ represents the constant offset necessary to make the zero level of the 
band $\nu_i$ map consistent with that of the 857 GHz map. For each band
$\nu_i$, we obtain estimates of $a$, $b$, and $c$ by performing a linear least 
squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatterplots of the band $\nu_i$ versus 857 GHz correlation
before and after correcting for the best-fit offset and residual dipole, for
each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the tightened 
correlations striking in these scatterplots, but the residual dipole 
subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
themselves. Before performing thermal dust fits, we therefore subtract the 
best-fit $c$ and $b\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.

>>>>

We have performed one regression per HFI band to simultaneously 
fit for the zero level offset, the slope relative to 857 GHz, and the residual 
dipole amplitude. For each 100-545 GHz HFI band, we restrict to regions of low
column density (H\,\textsc{i} $<$ 200 K\,km\,s$^{-1}$ for 
$-72$$<$$v_{LSR}$$<$$+25$ km\,s$^{-1}$) and fit the following model:

\begin{equation} \label{equ:dip}
\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_{p} + b
\end{equation}

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ gives the residual Solar dipole
amplitude, and its best-fit value represents the scaling of the Solar dipole 
that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
linear. $b$ represents the constant offset that must be subtracted from the 
band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
performing a linear least squares fit with uniform weights and iterative 
outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
versus 857 GHz correlation before and after correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatterplots, but the residual
dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
maps themselves. Before performing thermal dust fits, we therefore subtract the
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.

For \PLANCK~100 GHz, we found an additional low-order correction to be
necessary. Therefore, for 100 GHz, we performed a modified version of the 
Eqation \ref{equ:dip} fit, using the following model:

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = a\mathcal{I}_{857, p} + b\mathcal{D}_p + c + qQ_p
\end{equation}
